Very Preliminary Draft

### 2021-07-06 article/draft.tex
some changes

\begin{figure}
	\centering
		\begin{multicols}{1}
			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
		\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.29]{./img/oann/fig1_oann.png}
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/oann/fig2_oann.png} 
	\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.32]{./img/oann/fig3_oann.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tony/fig3_tony.png}
	\end{multicols}

@@

\begin{figure}
	\centering
		\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
		\end{multicols}

		\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/tony/fig2_tony.png}
		\end{multicols}
	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

@@

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_1.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/beautyoflife/fb_bl_2.png} 
	\end{multicols}

@@

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_1.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_2.png} 
	\end{multicols}

@@

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
	\end{multicols}

@@

\begin{figure}
	\centering
		\begin{multicols}{1}	
			\includegraphics[scale=0.35]{./img/globalresearch_2021-06-14.png}
		\end{multicols}

		\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
		\end{multicols}
		\caption{Screenshots taken on June 14, 2021. Top panel: screenshot that shows the account of $globalresearch.ca$ suspended on Twitter. Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.    }
		\label{fig3}
\end{figure}

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	\end{multicols}
\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Data collected via the Twitter API v2 on June $16$, 2021.   }
\label{fig4}
\end{figure}

\begin{figure}
\centering	
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
	\end{multicols}
\caption{}
\label{fig4bis}
\end{figure}

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 \end{multicols}
	\begin{multicols}{1} 
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
	\end{multicols}
	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
	\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
	\end{multicols}
	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
	\label{fig9}
\end{figure}

>>>>

\begin{figure}
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.2]{./img/fb/fig1_fb.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\begin{figure}
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.24]{./img/oann/fig1_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
	%\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.21]{./img/tony/fig3_tony.png}
	%\end{multicols}

@@

\begin{figure}
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.25]{./img/tony/fig1_tony.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.25]{./img/tony/fig2_tony.png}
		%\end{multicols}
	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/beautyoflife/fb_bl_2.png} 
	%\end{multicols}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_1.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/infowars/fb_infowars_2.png} 
	%\end{multicols}

@@

	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/infowars/fb_infowars_3.png}
	%\end{multicols}

@@

\begin{figure}
	\centering
		%\begin{multicols}{1}	
			\includegraphics[scale=0.35]{./img/globalresearch_2021-06-14.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/globalresearch_14_06_2021_16pm_UTC.png} 
		%\end{multicols}
		\caption{Screenshots taken on June 14, 2021. Top panel: screenshot that shows the account of $globalresearch.ca$ suspended on Twitter. Bottom panel: screenshot that shows that no results can be found when searching for $globalresearch.ca$.    }
		\label{fig3}
\end{figure}

@@

\begin{figure}
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	%\end{multicols}
\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Data collected via the Twitter API v2 on June $16$, 2021.   }
\label{fig4}
\end{figure}

\begin{figure}
\centering	
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
	%\end{multicols}
\caption{}
\label{fig4bis}
\end{figure}

@@

\begin{figure}
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
	%\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
	%\end{multicols}
	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
	\label{fig9}
\end{figure}
